valr: Reproducible genome interval analysis in R

### 2017-06-06 inst/paper/figs.Rmd
update fig color, size, names, and update manuscript

b <- bed_glyph(bed_merge(x)) + pub_theme
plot_grid(a, b, align = 'h', nrow = 1, labels="AUTO", scale = c(.9, .9))
ggsave("figure1.pdf", width = 8, height = 4)

@@

p <- ggplot(res, aes(x = .win_id, y = win_mean)) +
  geom_point(size = 0.25) + geom_pointrange(sd_limits, size = 0.1) + 
  scale_x_continuous(labels = x_labels, breaks = x_breaks) + 
  xlab('Position (bp from TSS)') + ylab('Signal') + 
  pub_theme +
  theme_classic()

plot_grid(p, align = 'h', nrow = 1, labels="AUTO")
ggsave("figure2.pdf", width = 3.5, height = 2.25)
```

@@

plot_grid(p, align = 'h', nrow = 1, labels="AUTO")
ggsave("figure3.pdf")

>>>>

b <- bed_glyph(bed_merge(x)) + pub_theme
plot_grid(a, b, align = 'h', nrow = 1, labels="AUTO", scale = c(.9, .9))
ggsave("figure1.pdf", width = 11.2, height = 5.6)

@@

p <- ggplot(res, aes(x = .win_id, y = win_mean)) +
  geom_point(size = 0.25) + geom_pointrange(sd_limits, size = 0.1) + 
  scale_x_continuous(labels = x_labels, breaks = x_breaks) + 
  xlab('Position (bp from TSS)') + ylab('Signal') + 
  theme_classic() +
  pub_theme

plot_grid(p, align = 'h', nrow = 1, labels="AUTO")
ggsave("figure2.pdf", width = 5.6, height = 4)
```

@@

plot_grid(p, align = 'h', nrow = 1, labels="AUTO")
ggsave("figure3.pdf", width = 5.6, height = 4)

### 2017-06-06 inst/paper/main.tex
update fig color, size, names, and update manuscript

R packages developed for interval analysis include IRanges \cite{lawrence_software_2013}, GenometriCorr [@Favorov12], and bedr \cite{haider_bedr_2016}. IRanges is a Bioconductor package that provides specialized interval classes and methods to conduct interval arthimetic and is utilized extensively by Bioconductor packages. GenometriCorr provides a set of statistical tests to determine the relationships between interval sets and builds upon IRanges. bedr is a CRAN distributed package that provides wrapper functions to call BEDTools, BedOPS, and tabix functions providing out-of-memory support for interval analysis in R. These packages provide important functionality for interval analysis in R however they do not easily integrate with interactive data visualization features developed for R, such as Shiny\cite{chang_shiny_2017}, and the RStudio IDE. Additionally, the programmatic advances provided by the recent tidyverse suite of data processing and visualization tools (dplyr, purrr, broom, and ggplot2) do not easily interface with the R S4 objects implemented in many Bioconductor packages for data organization \cite{wickham_tidyverse_2017}.

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{glyphs.pdf}
\caption{\label{fig:Figure 1}Visualizing interval operations in valr with \texttt{bed\_glyph()}.} 
\end{figure}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# calculate the mean of column 6 for intervals in `b` that overlap with `a`}
\KeywordTok{bedtools} \NormalTok{map -a a.bed -b b.bed -c 6 -o mean}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# calculate the mean and variance for a `value` column}
\KeywordTok{bed_map}\NormalTok{(a, b, }\DataTypeTok{.mean =} \KeywordTok{mean}\NormalTok{(value), }\DataTypeTok{.var =} \KeywordTok{var}\NormalTok{(value))}

\CommentTok{# report concatenated and max values for merged intervals}
\KeywordTok{bed_merge}\NormalTok{(a, }\DataTypeTok{.concat =} \KeywordTok{concat}\NormalTok{(value), }\DataTypeTok{.max =} \KeywordTok{max}\NormalTok{(value))}
\end{Highlighting}
\end{Shaded}

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{tss.pdf}
\caption{\label{fig:Figure 2}Meta-analysis of signals relative to genomic features with valr. \textnormal{Summarized coverage of human H3K4Me3 Chip-Seq coverage across positive strand transcription start sites. Data presented +/- SEM.}}
\end{figure}

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{benchmarks.pdf}
\caption{\label{fig:Figure 3} Performance of major valr functionality benchmarked against BEDTools \textnormal{Timings calculated using microbenchmark and GNU time commands for valr and BEDTools respectively (A).}}
\end{figure}

@@

\begin{figure}
\centering
    \begin{subfigure}[b]{0.45\textwidth}
\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{x <-}\StringTok{ }\KeywordTok{trbl_interval}\NormalTok{(}
  \NormalTok{~chrom, ~start, ~end,}
  \StringTok{'chr1'}\NormalTok{, }\DecValTok{25}\NormalTok{,     }\DecValTok{50}\NormalTok{,}
  \StringTok{'chr1'}\NormalTok{, }\DecValTok{100}\NormalTok{,    }\DecValTok{125}
\NormalTok{)}

@@

>>>>

R packages developed for interval analysis include IRanges \cite{lawrence_software_2013}, GenometriCorr \cite{favorov_exploring_2012}, and bedr \cite{haider_bedr_2016}. IRanges is a Bioconductor package that provides specialized interval classes and methods to conduct interval arthimetic and is utilized extensively by Bioconductor packages. GenometriCorr provides a set of statistical tests to determine the relationships between interval sets and builds upon IRanges. bedr is a CRAN distributed package that provides wrapper functions to call BEDTools, BedOPS, and tabix functions providing out-of-memory support for interval analysis in R. These packages provide important functionality for interval analysis in R however they do not easily integrate with interactive data visualization features developed for R, such as Shiny\cite{chang_shiny_2017}, and the RStudio IDE. Additionally, the programmatic advances provided by the recent tidyverse suite of data processing and visualization tools (dplyr, purrr, broom, and ggplot2) do not easily interface with the R S4 objects implemented in many Bioconductor packages for data organization \cite{wickham_tidyverse_2017}.

@@

@@

\begin{Highlighting}[]
\CommentTok{# calculate the mean of column 6 for intervals in `b` that overlap with `a`}
\KeywordTok{bedtools} \NormalTok{map -a a.bed -b b.bed -c 6 -o mean}
\end{Highlighting}

@@

\begin{Highlighting}[]
\CommentTok{# calculate the mean and variance for a `value` column}
\KeywordTok{bed_map}\NormalTok{(a, b, }\DataTypeTok{.mean =} \KeywordTok{mean}\NormalTok{(value), }\DataTypeTok{.var =} \KeywordTok{var}\NormalTok{(value))}

\CommentTok{# report concatenated and max values for merged intervals}
\KeywordTok{bed_merge}\NormalTok{(a, }\DataTypeTok{.concat =} \KeywordTok{concat}\NormalTok{(value), }\DataTypeTok{.max =} \KeywordTok{max}\NormalTok{(value))}
\end{Highlighting}

@@

@@

@@

%%%% Figure 1 %%%%

\begin{figure}[!htb]
\centering
\includegraphics[width=1\textwidth]{figure1.pdf}
\caption{\label{fig:Figure 1}Visualizing interval operations in valr with \texttt{bed\_glyph()}.} 
\end{figure}

%%%% Figure 2 %%%%

\begin{figure}[!htb]
\centering
\includegraphics[width=0.5\textwidth]{figure2.pdf}
\caption{\label{fig:Figure 2}Meta-analysis of signals relative to genomic features with valr. \textnormal{Summarized coverage of human H3K4Me3 Chip-Seq coverage across positive strand transcription start sites. Data presented +/- SEM.}}
\end{figure}

%%%% Figure 3 %%%%
\begin{figure}[!htb]
\centering
\includegraphics[width=0.5\textwidth]{figure3.pdf}
\caption{\label{fig:Figure 3} Performance of major valr functionality benchmarked against BEDTools \textnormal{Timings calculated using microbenchmark and GNU time commands for valr and BEDTools respectively (A).}}
\end{figure}

%%%% Table 1 %%%%

%%%%%%%%%%%% Previous Figures %%%%%%%%%%%

%%%% TSS H3K4me3 example %%%%
\begin{figure}
\centering
    \begin{subfigure}[b]{0.45\textwidth}
\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{x <-}\StringTok{ }\KeywordTok{trbl_interval}\NormalTok{(}
  \NormalTok{~chrom, ~start, ~end,}
  \StringTok{'chr1'}\NormalTok{, }\DecValTok{25}\NormalTok{,     }\DecValTok{50}\NormalTok{,}
  \StringTok{'chr1'}\NormalTok{, }\DecValTok{100}\NormalTok{,    }\DecValTok{125}
\NormalTok{)}

@@

%%%% DNA methylation example %%%%
